%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape RAJ MATHUR} \\ \vspace{1pt}
    \small +91 8340637097 $|$ \href{mailto:x@x.com}{\underline{rajmathur8409@gmail.com}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/raj-mathur-778181258/}} $|$
    \href{https://github.com/...}{\underline{github.com/Rajmathur-8}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {International Institute of Information Technology}{Bhubanewar, Odisha}
      {Bachelor of technology in Computer Science, 2nd year}{Nov. 2022 -- April 2026}
      
     { {CGPA - 7.54 (till 3rd sem)}}
      
    \resumeSubheading
      {Golden Bell Public School}{Bihar Sharif , Bihar}
      {Higher Secondary Education}{2019 - 2021}
      
      { {Percentage - 81.6  $%$}}

  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
%\section{Experience}
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    
%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Social media Backend } $|$ \emph{\textbf{ Spring boot, spring security, MySQL, JPA } }}{}
          \resumeItemListStart
            \resumeItem{Developed robust \textbf{backend} systems using \textbf{Spring Boot} to handle key functionalities like \textbf{post creation, liking, saving, reposting, and commenting,} ensuring smooth data flow and enhanced user engagement .}
            \resumeItem{ Implemented \textbf{real-time messaging} capabilities leveraging \textbf{Spring Security} and \textbf{WebSockets} for seamless and secure communication.}
            \resumeItem{Utilized \textbf{MySQL} for \textbf{database management}, ensuring efficient storage and retrieval of user data, posts, messages. Implemented \textbf{JPA and Hibernate for ORM,} streamlining database interactions and \textbf{maintaining data consistency.}}
             \resumeItem{Built comprehensive \textbf{user profile management} features allowing users to \textbf{update profiles} and \textbf{manage connections through follow/unfollow actions}, ensuring data integrity and security.}
          \resumeItemListEnd
     \resumeProjectHeading
          {\textbf{ online Delivery Backend $|$ Spring boot, spring security, MySQL, JPA }   } {}
% {march 2024}
          \resumeItemListStart
            \resumeItem{Led the development of an online food delivery app using \textbf{Spring Boot} for \textbf{backend services},  and \textbf{Spring Security with JWT} for robust \textbf{user authentication and secure session management.}}
             \resumeItem{Utilized \textbf{MySQL} for managing the app's \textbf{database}, ensuring efficient data storage, retrieval, and management. Implemented \textbf{JPA} and \textbf{Hibernate} for \textbf{ORM} (Object-Relational Mapping) to streamline database interactions. }
              \resumeItem{Implemented \textbf{role-based access control} to differentiate user permissions for \textbf{customers and owners}, providing personalized experiences and \textbf{secure data access}. }
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Todo Management App} $|$ \emph{\textbf{Java, SpringBoot, React, Jpa , Hibernate, Spring Security}}}
          
          \resumeItemListStart
            \resumeItem{Created a robust Todo application employing \textbf{Java, Spring Boot, Hibernate, React, and Spring Security.}}
             \resumeItem{Implemented \textbf{CRUD functionalities} ensuring seamless task management.}
              \resumeItem{Integrated Spring Security for\textbf{ authentication and authorization}, bolstering data security. }
               \resumeItem{Designed an intuitive user interface for enhanced user experience and developed\textbf{ RESTful APIs }for efficient data exchange between frontend and backend. }
                \resumeItem{Utilized\textbf{ agile methodologies} for iterative development cycles, ensuring rapid project progression and responsiveness to user feedback.}
           \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{\textbf{: Java, Python, C/C++, SQL (MySql), NoSQL( MongoDb), JavaScript, HTML/CSS, }} \\
     \item \textbf{Frameworks}{:}\textbf{ React, SpringBoot , JPA , Hibernate, Spring Security}
     \item  \\\textbf{Developer Tools}{:} \textbf{Git / Github , Docker, AWS, VS Code, Visual Studio, Eclipse, Intellij Idea}\textbf{, }canva, Codeblocks
     \item \textbf{Others}{:}\textbf{ REST APIs , Data Structures and Algorithms, OOPs,  DBMS, Problem Solving}\textbf{, Project Management, Leadership, Teamwork, Analytical Thinking}
    }}
 \end{itemize}
%-----------Achievements-----------
\section{Achievements}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{- Leetcode, rating - 1609 (350+ questions solved)} \\
     \textbf{- HACKATHON :  Hackfest (Top 4 out of 100+ teams)  Developed an end to end project for farmers by integrating ML and Blockchain technology.} \\
 {\textbf{- HACKATHON :   Smart Speedathon (Top 3) Developed an AI based ML model for College and Course recommendation system and made an end to end website for students integrating a chatbot.}
 \end{itemize}


%-------------------------------------------
\end{document}
